Finding Quality Issues in SKOS Vocabularies

### 2012-05-30 conclusions.tex
added acknowledgements section, adjusted todos
fixed some todos

We are aware that these issues are purely quantitative quality indicators. To learn more about the real-world impact of our work, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists. We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service. We also need to increase the performance and efficiency of our quality checking algorithms.

@@

\todo{add relative importance of the issues as future work}

>>>>

We are aware that these issues are purely quantitative quality indicators. To learn more about the real-world impact of our work like, e.g., the relative importance of the identified quality issues, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists. We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service. We also need to increase the performance and efficiency of our quality checking algorithms.

@@
